Rough Draft

### 2017-10-11 Article submission/roughdraft.tex
added an abstract + some edits to the introduction

@@

    Community-driven online question and answer forums (CQA) are becoming widely used sources of information. These online platforms allow for anyone to ask or answer a question. It provides a place for people of all backgrounds and levels of expertise to provide input on a certain question. One popular CQA is Yahoo! Answers, featuring questions of all topics and expertise levels. On the other hand of the spectrum is Stack Overflow, the CQA that features strictly computer programming question and answers. Forums liek these 2 recieve around 40 million visits every month. These online question and answer forums are clearnly becoming popular sources of information.

    The CQA analyzed in this paper is iFixit's Answers forum. iFixit is a company founded in 2003 by two engineering students of the California Polytechnic State University in San Luis Obispo. What began as a small business running out of the college dorms, is now a company that helps thousands of people fix their broken devices everyday, providing over 30,000 free repair guides with pictures and step-by-step instructions. iFixit also sells the specialized tools and parts used in their repair guides, specialized tools like an iPhone 7 batter adhesive strip or a Nexus 9 LCD screen and digitizer. The main goal of this company is to teach people how to fix their own devices, and in extending the lifetime of their own devices, they save money and cut down on electronic waste. As such, this company helps thousands of people fix their devices everyday.

    Along with repair guides and tool sales, another important component of this company is their online question and answer forum called Answers. This platform features questions related to device repair, featuring over 9,000 devices and over 100,000 solutions and answers. Questions on this forum range from broken devices like a jammed zipper on a Patagonia jacket, to a shattered iPhone 6 plus screen. This forum is an integral part in teaching people how to fix their own devices. If people run into problems, they can always trust that they have a large community to turn to for help. Thus it's important, for both the individuals as well as iFixit, that askers get prompt answers. Fast response times will drive up user engagement and generate more traffic, which in turn is great for the reputation and longevity of Answers and iFixit. As such, investigation of response times would be both beneficial and informative. Analysis can reveal factors within the forum that affect how quickly questions get answers.

    Suggestions for how users can ask questions to minimize answer times and for how the forum design can be improved, can be derived from such analysis. However, to the best of our knowledge, analysis and prediction of answer times on forums has not been investigated by many researchers. A majority of the research focuses on assessing and predicting the question and answer quality. As such, there is need for further analysis of response times in these forums. This paper presents a survival analysis on the time until a question is answered on iFixit's Answers forum. It attempts to determine the factors that are significantly related to answer time, and create a cox proportional hazards model that can accurately predict the survival probability of a question.

>>>>

\section{Abstract}

Community-driven online question and answer forums (CQA) are becoming increasingly valuable sources of information. These platforms house an expansive amount of crowd-sourced knowledge in the form of thousands of questions and answers posted everyday. There are forums that cover a broad range of topics, like Yahoo! Answers, and forums focused on specific topics, like computer programming-focused Stack Overflow. An example of the latter is iFixit's CQA, Answers. As the main goal of iFixit is to teach people to fix their own devices by providing them with the knowledge and tools necessary, Answers---featuring questions related specifically to device repair---is a valuable source of information for this community. Thus, it's important that questions receive answers, and receive them quickly. This paper presents a survival analysis on the time until a question recieves its first answer. We developed a cox proportional hazards model to predict the failure probability of a question, or the probability that a question receives an answer before a certain time. Though our model was signficant, its predictive accuracy was low. Our findings indicate that the most important predictors were the device category of the question (questions pertaining to Apple products receiving answers faster than others), and factors related to the question's title (e.g., whether or not it's phrased as a question, or if it contains terms considered ``unpopular''). For future studies, our findings can be applied to other models and further analysis of answer times in CQA.

@@

    Community-driven online question and answer forums (CQA) are becoming widely used sources of information. These online platforms allow for anyone to ask or answer a question. It provides a place for people of all backgrounds and levels of expertise to provide input on a certain question. One popular CQA is Yahoo! Answers, featuring questions of all topics and expertise levels. On the other hand of the spectrum is Stack Overflow, the CQA that features strictly computer programming question and answers. Forums like these 2 receive around 40 million visits every month. These online question and answer forums are clearly becoming popular sources of information.

    The CQA analyzed in this paper is iFixit's Answers forum. iFixit is a company founded in 2003 by two engineering students of the California Polytechnic State University in San Luis Obispo. What began as a business running out of the college dorms, is now a company that helps thousands of people fix their broken devices everyday, providing over 30,000 free repair guides with pictures and step-by-step instructions. iFixit also sells the specialized tools and parts needed for such repairs---tools like iPhone 7 battery adhesive strips or a Nexus 9 LCD digitizers. The main goal of this company is to provide people with the help and tools they might need to repair their devices, and in teaching people how to extend the lifetime of their devices, it allows people to save money and cut down on electronic waste.

    Along with repair guides and tool sales, another important component of this company is the online question and answer forum, Answers. This platform features questions related to device repair, featuring over 9,000 devices and over 100,000 solutions and answers. Questions on this forum range from broken devices like a jammed zippers to shattered iPhone screens. This forum is an integral part in teaching people how to fix their own devices. If people run into problems, they can always trust that they have a large community to turn to for help. Thus it's important, for both the individuals as well as iFixit, that askers get prompt answers. Fast response times will drive up user engagement and generate more traffic, which in turn is great for the reputation and longevity of Answers and iFixit. As such, investigation of response times would be both beneficial and informative. Analysis can reveal factors within the forum and from elements of the questions, that affect how quickly questions get answers. Suggestions for how users can ask questions to minimize answer times and for how the forum design can be improved, can be derived from such analysis.

    However, to the best of our knowledge, analysis and prediction of answer times on forums has not been investigated by many researchers. A majority of the research focuses on assessing and predicting the question and answer quality. As such, there is need for further analysis of response times in these forums. This paper presents a survival analysis on the time until a question is answered on iFixit's Answers forum. It attempts to determine the factors that are significantly related to answer time, and create a cox proportional hazards model that can accurately predict the failure probability of a question.
